### 2023-12-20 conclusions/imag.tex
New text, missing societal

The potential chip that would be created has been analyzed, there are also other aspects to take into account. The system being a way to run a wide variety of \acp{NN}, depending on the scale of the project the cip is used in, the impact of training is different. However, the main application being for embedded systems, training the system for a few hours is negligible when the final circuit is used thousands to millions times in its life cycle.
The inference of the \ac{NN} also has an environmental impact due to the power it uses. But the goal of building an analog \ac{NN} is to reduce both execution time and energy consumption, and while the energy comsumption wasn't evaluated in this thesis

Subtantial gain in power consumption.

@@

>>>>

The potential chip that would be created has been analyzed, there are also other aspects to take into account. The system being a way to run a wide variety of \acp{NN}, depending on the scale of the project the cip is used in, the impact of training is different. However, the main application being for embedded systems, training the system for a few hours is negligible when the final circuit is used thousands to millions times in its life cycle.
The inference of the \ac{NN} also has an environmental impact due to the power it uses. But the goal of building an analog \ac{NN} is to reduce both execution time and energy consumption, and while the energy comsumption wasn't evaluated in this thesis, it can be assumed, from the usual trend of analog circuits, a much lower energy consumption than with digital chips. This, scaled with thousands of units, offers a subtantial gain in overall power consumption.

Once again, the system having a wide spectrum of applications, the rebound effect can't be determined, it all depends on the kind of \ac{NN} that will be running on the chip. Nonetheless, the system being designed around embedded systems, the improvements made to the power consumption will affect the battery life of the product using the chip.

@@

The societal impacts are hard t
